Early Observations of \abc:\\ \textbf{a Type Ia Supernova Featuring Either} Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-11-16 doc/ms.tex
acknowledge the referee

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.48\textwidth]{Branch_vel_evol.pdf}
  \caption{\textbf{Velocity evolution of \ion{Si}{2},   
           $v_{\mathrm{Is\,II}\,\lambda6355}$, for \abc\ compared to the median
           evolution of the four spectroscopic subclasses defined in
           \citet{2006PASP..118..560B}, using data from
           \citet{2012AJ....143..126B}. Typical uncertainties for \abc\ are
           $\sim$1000\,km\,s$^{-1}$ before $T_{B,\mathrm{max}}$, when the
           \ion{Si}{2}$\,\lambda6355$ profile is shallow and the minimum of
           absorption is difficult to determine, and $\sim$300\,km\,s$^{-1}$
           after $T_{B,\mathrm{max}}$. For the median curves, the typical
           scatter, determined via the interquartile range of the sample, is
           $\sim$700\,km\,s$^{-1}$, around $T_{B,\mathrm{max}}$.
           At early times, core-normal and broad-line SNe have significantly
           faster \ion{Si}{2} than \abc, while the declining trend of coolSNe
           does not match \abc.}
  }
  \label{fig:branch_vel}
\end{figure}

@@

We are deeply grateful to R.~C.~Thomas for indulging a slew of questions regarding \ion{C}{2} in SNe. Similarly, it is our pleasure to buy a beer for R.~Amanullah and U.~Feindt for discussions regarding SALT2.

>>>>

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.48\textwidth]{Branch_vel_evol.pdf}
  \caption{\textbf{Velocity evolution of \ion{Si}{2},   
           $v_{\mathrm{Is\,II}\,\lambda6355}$, for \abc\ compared to the median
           evolution of the four spectroscopic subclasses defined in
           \citet{2006PASP..118..560B}, using data from
           \citet{2012AJ....143..126B}. Typical uncertainties for \abc\ are
           $\sim$1000\,km\,s$^{-1}$ before $T_{B,\mathrm{max}}$, when the
           \ion{Si}{2}$\,\lambda6355$ profile is shallow and the minimum of
           absorption is difficult to determine, and $\sim$300\,km\,s$^{-1}$
           after $T_{B,\mathrm{max}}$. For the median curves, the typical
           scatter, determined via the interquartile range of the sample, is
           $\sim$700\,km\,s$^{-1}$, around $T_{B,\mathrm{max}}$.
           At early times, core-normal and broad-line SNe have significantly
           faster \ion{Si}{2} than \abc, while the declining trend of cool SNe
           does not match \abc.}
  }
  \label{fig:branch_vel}
\end{figure}

@@

\textbf{This study has benefited from the suggestions of an anonymous
referee.} We are deeply grateful to R.~C.~Thomas for indulging a slew of
questions regarding \ion{C}{2} in SNe. Similarly, it is our pleasure to buy a
beer for R.~Amanullah and U.~Feindt for discussions regarding SALT2.
